Lyman-alpha spectra from rotating outflows

### 2018-03-13 paper/paper.tex
fixing paper plots

We evaluate first the effects of increasing rotational
velocity at fixed values of the optical depth and outflow velocity.
Figure \ref{fig:varying_rotation_small} summarizes the information.
All plots correspond to the same outflow velocity of $\vout=50$\kms,
rows have constant optical depth and columns have constant rotational
velocity.
Each panel shows different morphologies corresponding to varying
line-of-sight viewing angle.

@@

We now evaluate the effects of increasing outflow velocity at fixed
values for the optical depth and rotational velocity.
Figure \ref{fig:varying_outflow} summarizes the information following
the same patters as Figure \ref{fig:varying_rotation}, only that this
time all plots correspond to the same rotation velocity of
$\vrot=50$\kms.

@@

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/mean_line_7}
	\end{center}
	\caption{\textbf{Mean line for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:mean_line}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/standard_deviation_7}
	\end{center}
	\caption{\textbf{Standard Deviation for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.65\textwidth]{./figures/results/skewness_7}
	\end{center}
	\caption{\textbf{Skewness for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:skewness}}
\end{figure*}

>>>>

We evaluate first the effects of increasing rotational
velocity at fixed values of the optical depth and outflow velocity.
Figure \ref{fig:varying_rotation_small} summarizes its behavior 
(for largest range see Figure \ref{fig:varying_rotation}).
All plots correspond to the same outflow velocity of $\vout=50$\kms,
rows have constant optical depth and columns have constant rotational
velocity.
Each panel shows different morphologies corresponding to varying
line-of-sight viewing angle.

@@

We now evaluate the effects of increasing outflow velocity at fixed
values for the optical depth and rotational velocity.
Figure \ref{fig:varying_outflow_small} summarizes its behavior
(for largest range see Figure \ref{fig:varying_outflow}).
All plots correspond to the same rotation velocity of
$\vrot=50$\kms.

@@

\begin{figure}
	\begin{center}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_mn_vout5_logtau7}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_mn_vout25_logtau7}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_mn_vout50_logtau7}
	\end{center}
	\caption{\textbf{Mean line for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:mean_line}}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_std_vout5_logtau7}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_std_vout25_logtau7}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_std_vout50_logtau7}
	\end{center}
	\caption{\textbf{Standard Deviation for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:standard_deviation}}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
		\includegraphics[width=0.15\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
	\end{center}
	\caption{\textbf{Skewness for RT and DS:} The dots represent the Radiative 
		Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
		\label{fig:skewness}}
\end{figure}
